\documentclass[11pt, twoside]{report}

\usepackage{fontspec}
\usepackage[utf8]{inputenc}
\usepackage[bitstream-charter]{mathdesign}
\usepackage{bbding}
\usepackage{ragged2e}
\usepackage{parskip}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{paracol}
\usepackage{mdframed}
\usepackage[margin=1in]{geometry}

\usepackage[autocompile]{gregoriotex}

\titleformat{\chapter}[block]{\huge\scshape\filcenter}{}{1em}{}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{}{1em}{}

\mdfsetup{skipabove=\topskip, skipbelow=\topskip}

\newcommand{\rubric}[1]{
	\switchcolumn[0] {
		\itshape
		#1
	}
}

\newcommand{\latinenglish}[2]{
	\switchcolumn[0]* {
		#1
	}
	\switchcolumn[1] {
		\itshape\small
		#2
	}
}

\newcommand{\latinenglishequal}[2]{
	\switchcolumn[0]* {
		#1
	}
	\switchcolumn[1] {
		\itshape
		#2
	}
}

\newenvironment{latinenglishsection}
	{\columnratio{.7, .3} \begin{paracol}{2}}
	{\end{paracol}}

\newenvironment{latinenglishequalsection}
	{\columnratio{.5, .5}\begin{paracol}{2}}
	{\end{paracol}}

\setlength{\columnseprule}{0.4pt}

\newcommand{\heading}[1]{
	\begin{leftcolumn}
		#1
	\end{leftcolumn}
}

\newcommand{\spanning}[1]{
	\switchcolumn*[#1]
}

\newenvironment{verses}[1]
	{\begin{flushleft} \begin{enumerate}[leftmargin=*] \setcounter{enumi}{#1}}
	{\end{enumerate} \end{flushleft}}

\newenvironment{versicles}{\par\leavevmode\parskip=0pt}{}

\newenvironment{collect}
{
	\leavevmode
	\parindent=1em
	\parskip=0pt
	\noindent Orémus.\par
}{}

\newenvironment{optionbox}
{
	\switchcolumn[0]
	\begin{mdframed}
%	\begin{minipage}{0.8\linewidth}
}{
%	\end{minipage}
	\end{mdframed}
}

\newcommand{\optionrule}{
	\begin{center}
	\rule{0.5\linewidth}{0.6pt}
	\end{center}
}

\newenvironment{optionruled}
{
	\optionrule
}
{
	\optionrule
}

% for use inside the collect environment
\newcommand{\Amen}{\par\noindent \Rbar. Amen.}

\begin{document}

\section*{Salve Regina (Simple Tone)}

\textit{This Marian anthem is sung from First Vespers of Trinity Sunday (inclusive) until Vespers of the Saturday before the First Sunday of Advent (exclusive).}

\gresetinitiallines{1}
\gregorioscore{salve-regina-simple}

\begin{versicles}
\Vbar. Ora pro nobis, sancta Dei Génitrix.

\Rbar. Ut digni efficiámur promissiónibus Christi.
\end{versicles}

Orémus.
Omnípotens sempitérne Deus, qui gloriósæ Vírginis Matris Maríæ corpus et ánimam,
ut dignum Fílii tui habitáculum éffici mererétur, Spíritu Sancto cooperánte, præparásti:~\GreDagger\
da, ut cujus commemoratión\textit{e læ}\textbf{tá}mur,~*
ejus pia intercessióne ab instántibus malis et a morte perpétua liberémur.
Per eúmdem Christum Dóminum nostrum.

\gresetinitiallines{0}
\gabcsnippet{
(c3) <sp>R/</sp>. A(g.)men.(h.) (::)
}


\par\noindent\rule{\textwidth}{0.4pt}

Hail holy Queen, Mother of mercy, our life, our sweetness, and our hope.
To thee do we cry, poor banished children of Eve;
to thee do we send up our sighs, mourning and weeping in this valley of tears.
Turn then, O most gracious advocate, thine eyes of mercy towards us,
and after this our exile, show unto us the blessed fruit of thy womb, Jesus.
O clement, O loving, O sweet virgin Mary.

Pray for us, O holy Mother of God.
\Rbar.~That we may be made worthy of the promises of Christ.

Let us pray.
O almighty everlasting God, who, by the cooperation of the Holy Ghost,
didst prepare the body and soul of Mary, glorious Virgin and Mother,
to become the worthy habitation of Thy Son;
grant that we may be delivered from present evils and from everlasting death by her pious intercession,
in whose commemoration we rejoice.
Through the same Christ our Lord.
\Rbar.~Amen.

\end{document}